Observed vs. Simulated Year Comparison

### 2023-03-09 03-post-process/compare-sim-to-obs.Rmd
Remove unneeded content from sim-v-obs

# param = "phi_O0_Rb_BON[year,origin,pop]"
# obs_y_use = obs_sar_y
# sim_y_use = sim_sar_y
# origin = 1
# main = "main"

@@

  obs_vals = post_summ(post, sub_index(param, year = obs_y_use, ...))
  sim_vals = post_subset(post, sub_index(param, year = sim_y_use, ...), matrix = TRUE)
  # obs_vals = post_summ(post, sub_index(param, year = obs_y_use, pop = 1, origin = 1))
  # sim_vals = post_subset(post, sub_index(param, year = sim_y_use, pop = 1, origin = 1), matrix = TRUE)

>>>>

@@

  obs_vals = post_summ(post, sub_index(param, year = obs_y_use, ...))
  sim_vals = post_subset(post, sub_index(param, year = sim_y_use, ...), matrix = TRUE)
